\begin{abstract}

%Ceph is designed to be a reliable and scalable fault tolerant parallel file
%system with a number of intriguing features. 

Ceph is an open-source and emerging distributed parallel file and storage
system technology. It is designed to provide file system-level and object-level
access to data. Ceph, by design, assumes running on unreliable and commodity
storage and network hardware and provides reliability and fault-tolerance
through pre-calculated and controlled object placement and data replication. 

In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
technology for future high-performance computing (HPC) environments, like ours.
This paper presents our evaluation methodology, experiments, results and
observations from mostly parallel I/O performance and scalability perspectives.
Our work made two unique contributions. First, our evaluation is performed
under a realistic setup for a large-scale capability HPC environment like ours
using a commercial high-end storage system (Data Direct Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability, and
performance. These changes should also benefit the Ceph and HPC community at
large. Throughout the evaluation, we observed that Ceph still is an evloving
technology and is under fast-paced development and maturing with great promise. 

\end{abstract}
